\documentclass[10pt]{article}
\usepackage{fullpage, url}
\usepackage{amsmath}
\usepackage{amsfonts, amssymb, mathrsfs,fancyhdr}
\usepackage{slantsc}
\usepackage{titlesec}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\titleformat{\section}
  {\normalfont\fontsize{12}{15}\bfseries}{\thesection}{1em}{}
\setlength{\parindent}{0in}

\begin{document}
\begin{center}
{\Large{\bf{Matthew J. Keefe}}}\\
\end{center}
\underline{\hspace{7.3in}}\\
~~\\
8036 Bowery Drive  \hfill Phone: (302) 530-6553\\
Winter Garden, FL 34787 \hfill Email: matthew.j.keefe@gmail.com\\
\underline{\hspace{7.3in}}
\section*{EDUCATION}
\begin{itemize}
\item[] {Ph.D.} in Statistics,  Virginia Tech, Blacksburg, VA, 2017  
%\mbox{~~~~~}Overall GPA: 3.93/4.00 
\item[] {M.S.} in Statistics, Virginia Tech, Blacksburg, VA, 2013 
\item[] { B.S.} in Mathematics, Millersville University of Pennsylvania, Millersville, PA, 2012\\
\mbox{~~~~~}Minor in Computer Science
%\mbox{~~~~~}Overall GPA: 3.90/4.00 \hspace{12pt} Major GPA: 4.00/4.00 
\end{itemize}

\section*{COMPUTER SKILLS}
\begin{itemize}
\item[] R, Python, Git, SQL, Docker, SAS, \LaTeX, Tableau, Microsoft Office 
\end{itemize}

\section*{WORK EXPERIENCE}
\begin{itemize}
\item[] \textbf{The Walt Disney Company, Orlando, FL\\
Manager, Decision Science, September 2022 - Present \\
Sr. Decision Scientist, February 2020 - September 2022 \\
Decision Science Consultant, June 2017 - February 2020}
\begin{itemize}
\item Explored, developed, and sustained statistical models for demand forecasting and pricing used for client decision support across several technical projects in applications including yield management, media viewership, media advertisement sales, and other ad hoc analyses 
\item Engaged in technical requirement discussions with client teams for complex projects comprised of several scientific modules that use mathematical and statistical methodology
\item Designed and executed regularly running batches of science code using GitLab, Docker, Python, and R to deliver science output to clients
\item Led recruiting, interviewing, onboarding, and event planning for the department professional intern program in addition to overseeing technical project work for several interns
\item Developed and delivered educational content to business professionals on data science topics, including data visualization, R programming, and probability \& uncertainty in business decision making
\item Led a team of data science experts to develop and deliver an data and analytics curriculum consisting of 21 courses for finance professionals reaching over 4,000 individuals across the company
\item Created and facilitated an analytics programming user group of over 100 members across many analytical teams within the company to promote and share coding best practices
%\item Implemented sophisticated statistical modeling for pricing of advertisement sales for Freeform, ABC, A\&E Networks, and ESPN
%\item Developed software solutions using statistics and optimization to drive revenue for The Walt Disney Company
\end{itemize}

\item[] \textbf{Laboratory for Interdisciplinary Statistical Analysis (LISA), Blacksburg, VA\\
LISA Collaborator, August 2014 - May 2017}
\begin{itemize}
\item Collaborated with clients to answer key research questions in a wide variety of areas involving applications of statistical methodology, such as geology, housing research, ecology, agriculture, and engineering
%\item Collaborated with clients to help answer important research questions using statistics 
\end{itemize}


\item[] \textbf{Virginia Tech Department of Statistics, Blacksburg VA\\
Course Instructor, April 2014-August 2014, Summer 2015, Summer 2016 - May 2017}
\begin{itemize}
\item Led lectures for undergraduate statistics courses
\item Created all course materials (notes, quizzes, homework, exams) for three courses
\end{itemize} 
 
 
\item[] \textbf{Virginia Center for Housing Research, Blacksburg, VA\\
Graduate Research Assistant, December 2012 - May 2015}
\begin{itemize} 
\item Provided statistical consulting to research team members
%\item Managed the Builder Practitioner Survey data
\item Constructed and interpreted statistical models for the diffusion of green technology in the housing market
\end{itemize} 

\item[] \textbf{Eastman Chemical Company, Kingsport, TN\\
Applied Statistics Group Intern, Summer 2013}
\begin{itemize}
\item Broadened knowledge of applications of statistics in industry
\item Assisted clients with design of experiments, statistical process monitoring, and statistical analysis
%\item Applied statistical concepts to a wide variety of industrial projects
\end{itemize} 


\item[] \textbf{Virginia Tech Department of Statistics, Blacksburg, VA\\
Graduate Teaching Assistant, August 2012 - December 2012}
\begin{itemize}
\item Explained key statistical concepts to undergraduate students during office hours
%\item Offered helpful feedback to students when grading homework assignments
\end{itemize}

%\item[] \textbf{Millersville University Office of Assessment, Planning, and Institutional Research, Millersville, PA \\
%Intern, August 2011 - May 2012}
%\begin{itemize}
%\item Analyzed institutional survey data in order to improve the university
%\item Produced figures, tables, and reports for various statistical analyses of institutional survey data
%\end{itemize}


%\item[] \textbf{University of Pittsburgh SIBS (Summer Institute for Training in Biostatistics), Pittsburgh, PA \\
%Student, Summer 2011}
%
%
%\item[] \textbf{Sylvan Learning Center, Newark, DE \\
%Math Teacher, Summer 2010 - Summer 2011} 
\end{itemize}


\section*{TEACHING EXPERIENCE}
\begin{itemize}
%\item Guest Lecturer: Communication in Statistical Collaborations, February 2016
%\item LISA Short Course: Visualizing and Analyzing Spatial Data with R, December 2015
\item STAT 4714: Probability and Statistics for Electrical Engineers, Summer 2014, 2015, 2016, Fall 2016, Spring 2017
\item STAT 4706: Probability and Statistics for Engineers II, Summer 2014
\item STAT 2004: Introductory Statistics, April 2014-May 2014
\end{itemize}


\section*{PEER-REVIEWED PUBLICATIONS}
\begin{itemize}
 \item[] \textbf{Keefe, M.J.}, Ferreira, M.A.R., \& Franck, C.T. (2019). Objective Bayesian Analysis for Gaussian Hierarchical Models with Intrinsic Conditional Autoregressive Priors. \textit{Bayesian Analysis} 14(1):181-209.
 
 \item[] \textbf{Keefe, M.J.}, Ferreira, M.A.R., \& Franck, C.T. (2018). On the formal specification of sum-zero constrained intrinsic conditional autoregressive models. \textit{Spatial Statistics} 24:54-65.
 
 \item[] Sanderford, A.R., McCoy, A.P., \& \textbf{Keefe, M.J.} (2018). Adoption of Energy Star certifications: theory and evidence compared. \textit{Building Research \& Information} 46(2):207-219.
 
 \item[] \textbf{Keefe, M.J.}, Loda, J.B., Elhabashy, A.E., \& Woodall, W.H. (2017). Improved Implementation of the Risk-adjusted Bernoulli CUSUM Chart to Monitor Surgical Outcome Quality. \textit{International Journal for Quality in Health Care} 1-6.
 
\item[] \textbf{Keefe, M.J.}, Franck, C.T., \& Woodall, W.H. (2017). Monitoring Foreclosure Rates with a Spatially Risk-adjusted Bernoulli CUSUM Chart for Concurrent Observations. \textit{Journal of Applied Statistics} 44(2):325-341.

\item[] Clark, E.V., Zipper, C.E., Daniels, W.L., Orndorff, Z.W., \textbf{Keefe, M.J.} (2017) Modeling Patterns of Total Dissolved Solids Release from Central Appalachia, USA Mine Spoils. \textit{Journal of Environmental Quality} 46(1):55-63.

\item[] \textbf{Keefe, M.J.}, Woodall, W.H., \& Jones-Farmer, L.A. (2015). The Conditional In-Control Performance of Self-Starting Control Charts. \textit{Quality Engineering} 27(4):488-499.

\item[] Saleh, N.A., Mahmoud, M.A., \textbf{Keefe, M.J.}, \& Woodall, W.H. (2015). The difficulty in designing Shewhart $\bar{X}$ and X control charts with estimated parameters. \textit{Journal of Quality Technology} 47(2):127-138.

\item[] McCoy, A.P., Koebel, C.T., Sanderford, A.R., Franck, C.T., \& \textbf{Keefe, M.J.} (2015). Adoption of High-Performance Housing Technologies Among US Homebuilding Firms, 2000 Through 2010. \textit{Cityscape: A Journal of Policy Development and Research}, 17(2).

\item[] Koebel, C.T., McCoy, A.P., Sanderford, A.R., Franck, C.T., \& \textbf{Keefe, M.J.} (2015). Diffusion of Green Building Technologies in New Housing Construction. \textit{Energy and Buildings}, 97:175-185.

\item[] Sanderford, A.R., \textbf{Keefe, M.J.}, Koebel, C.T., \& McCoy, A.P. (2015). Factors Influencing U.S. Homebuilders' Adoption of Green Homebuilding Products. \textit{Journal of Sustainable Real Estate}, 7(1):60-82.

\end{itemize}

\section*{AWARDS \& HONORS}
\begin{itemize}
\item 2016-2017 Virginia Tech Graduate Student of the Year Award Finalist
\item 2016-2017 Ellis R. Ott Scholarship Winner (PhD category)
\item Klaus Hinkelmann Award for outstanding service within the Department of Statistics at Virginia Tech, 2015-2016
\item 2016 Outstanding LISA Collaborator of the Year
%\item 2015 Outstanding LISA Collaborator of the Year Finalist
\item William Byer Award for outstanding service to the Department of Statistics at Virginia Tech, Fall 2015
\item Rose Costain Award for outstanding citizenship by a graduate student within the Department of Statistics at Virginia Tech, 2014-2015
%\item American Real Estate Society Best Paper for Sustainable Real Estate, 2014
%\item $57^{th}$ Annual Fall Technical Conference Student Grant, October 2013
%\item Inducted into Mu Sigma Rho: National Statistical Honor Society, Virginia Tech, September 2013
%\item Corporate Partners Scholarship, Virginia Tech, August 2012 
%\item Harry E. Canter Statistics Award, Millersville University, Fall 2011-Spring 2012
%\item Edna Myers Mathematics Scholarship, Millersville University, Fall 2010-Spring 2012

\end{itemize}

%\section*{SERVICE}
%\begin{itemize}
%\item Vice President of Mu Sigma Rho: National Statistical Honor Society, Virginia Tech Chapter, Fall 2015-Spring 2016
%\item Committee Member for Virginia Tech Department of Statistics Corporate Partners Conference, Spring 2014-Present
%\item President of Statistics Graduate Student Assembly, Virginia Tech, Spring 2013-Spring 2016
%\item Private Tutor for Virginia Tech Department of Statistics, Fall 2013-Present
%\end{itemize}

%\section*{References available upon request}

\end{document}




